### 2024-11-14 README.Rmd
update README

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

@@

@@

The goal of hatchR is to allow users to leverage daily temperature records to predict when a fish is expected to hatch and/or emerge using statistical models

@@

``` r
# install.packages("pak")
pak::pak("bmait101/hatchR")
```

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

@@

## Overview

@@

hatchR is a tool that allow users to leverage daily temperature records to predict when a fish is expected to hatch and/or emerge using statistical models.

Specifically, hatchR is intended to bridge the analytic gap of taking statistical models developed in hatchery settings (e.g., Beacham and Murray 1990) and applying them to real world temperature data sets using the effective value framework developed by Sparks et al. (2019).

@@

``` r
# install.packages("pak")
pak::pak("bmait101/hatchR")
```
## Usage

## Getting help

If you encounter a clear bug, please file an issue with a minimal reproducible example on [GitHub](https://github.com/bmait101/hatchR/issues). For questions and other discussion, please reach out to the package authors: [Morgan Sparks](morgan.sparks@usda.gov), [Bryan Maitland](bryan.maitland@usda.gov).
